---
title: "Inferences Mikey"
format: html
embed-resources: true
---

```{r}
#| label: setup
#| message: false
#| warnings: False

library(tidyverse)
library(gt)
library(modeldata)
Carseats<-ISLR2::Carseats
```
**Problem 1**


```{r}
t.test(Carseats$Price)

#|alt-text: A boxplot showing the Prices from the main manufacturer
ggplot(Carseats, aes(Price))+
  geom_boxplot(fill="Orange")+
  scale_x_continuous(breaks = seq(25,195, by=15))+
  theme_minimal()
```

The current hypothesis is that mean price for car seats from the main manufacture is 110
$H_0: \mu = 110$
The alternative would be that the mean price is anything else other then 110
$H_A: \mu \neq 110$

As we can see in this Box plot and the T-test the price of car seats from the main manufacturer is ~115.79 the most of the car seats falling in between ~113.47 and ~118.12. So if you really want to get a car seat for 110 you'll have to look somewhere else 


**Problem 2**
```{r}
t.test(Carseats$CompPrice, conf.level = .90)
Error<-(124.975-123.7109)
```
Sadly this one is more then 110 too 

**Problem 3**
```{r}
table_peng<- table(penguins$species,penguins$island)

addmargins(table_peng)
```

**Problem 4**

https://github.com/Mikey0296/Math-250-sandbox.git